Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:14	12:25:36	(Wed14.Oct)

We propose using a light weight alternative to MVDR called the Low Complexity Adaptive (LCA) beamformer. It was first introduced by Synnev\aa{}g in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar results to MVDR in a system with focused transmit beams. LCA applies a set of predefined windows, or tapers, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a delay-and-sum (DAS) beamformer with an adaptive multi-taper extension. Such extensions have been studied in e.g. radar imaging up to \cite{Stankwitz1995}, but unlike these

Synnev\aa{}g used a window set comprised of rectangular, Kaiser and inverted Kaiser functions\footnote{May also be called Kaiser-Harris windows.}. He made LCA choose from 12 unique windows, 6 of which were micro-steered variants of a fairly wide Kaiser window. While achieving good results, it was not made clear how LCA performs with more or fewer windows, and how steering affects it all.

>>>>

A very fast and simple alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. It was first introduced by Synnev\aa{}g in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar results to MVDR in a system with focused transmit beams\todo{ha med at i US \o{}nsker man ulike vindus-typer p\aa{} forskjellig range?}. LCA applies a set of predefined windows, or tapers, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a delay-and-sum (DAS) beamformer with an adaptive multi-taper extension. Such extensions up to 3 windows by e.g. Stankwitz in radar imaging~\cite{Stankwitz1995}, but unlike these LCA more windows, and add micro-steered variations of them.

Synnev\aa{}g used a window set comprised of rectangular, Kaiser (or Kaiser-Harris) and inverted Kaiser functions. He made LCA choose from 12 unique windows, 6 of which were micro-steered variants of a fairly wide Kaiser window. While achieving good results, it was not made clear how LCA performs with more or fewer windows, and how steering affects it all. His system
